\chapter*{Proforma}

{%
\begin{tabular}{ll}
Name:               & \bf Dhruv Makwana \\
College:            & \bf Trinity College                     \\
Project Title:      & \bf Exploring the structure of mathematical theories \\
                    & \bf using graph databases \\
Examination:        & \bf Computer Science Tripos, Part II, 2016--2017 \\
Word Count:         & \bf 11,044 \\
Project Originator: & Dr.\ Timothy G. Griffin \\
Supervisor:         & Dr.\ Timothy G. Griffin \\
\end{tabular}
}

\section*{Original Aims of the Project}

This project aims to (a) represent Coq libraries as Neo4j (graph) databases and
(b) create a library of Neo4j tools with the goal of highlighting the structure
and relationship between the representations of the proof-objects.  It also
aims to have more features but still perform comparably to existing tools which
help a user understand a Coq library. As an extension, this project aims to
work with the Odd Order Theorem (part of Mathematical Components Coq library).

\section*{Work Completed}

This project represents Coq libraries as Neo4j (graph) databases and provides a
library of Neo4j tools that highlighting the structure of and relationship
between proof-objects. It performs comparably to existing tools which help a
user understand a Coq library. This project works with the Odd Order Theorem
(part of Mathematical Components Coq library) extension task.

\section*{Special Difficulties}
None.

\newpage
\section*{Declaration}

I, Dhruv Makwana of Trinity College, being a candidate for Part II of the
Computer Science Tripos, hereby declare that this dissertation and the work
described in it are my own work, unaided except as may be specified below, and
that the dissertation does not contain material that has already been used to
any substantial extent for a comparable purpose.

\bigskip
\leftline{\textbf{Signed}: Dhruv Makwana}

\bigskip
\leftline{\textbf{Date}:\date}
