\chapter{Implementation}

{\sf \color{red}
  This chapter should describe what was actually produced: the programs which
  were written, the hardware which was built or the theory which was developed.
  Any design strategies that \textbf{looked ahead to the testing stage} might profitably
  be referred to (the professional approach again). 

  Descriptions of programs may include fragments of high-level code but large
  chunks of code are usually best left to appendices or omitted altogether.
  Analogous advice applies to circuit diagrams. 

  \textbf{Draw attention to the parts of the work which are not your own}. Making
  effective use of powerful tools and pre-existing code is often laudable, and
  will count to your credit if properly reported. 

  It should not be necessary to give a day-by-day account of the progress of the
  work but \textbf{major milestones may sometimes be highlighted with advantage}.
}

\section{Coq object-files to CSV}
Intention, execution, problems (remember the stack overflow), solutions.

Also, how it fit in with larger, open-source projects.

\subsection{Model}

\subsubsection{Initial}

\subsubsection{Removed}

\subsubsection{Precise Kinds}

\subsubsection{Recursive Modules}

\subsubsection{Types}

\subsubsection{Relationships}

\begin{itemize}
  \item Tried and \emph{removed} x\_USED\_BY\_y
  \item USES
  \item CONTAINS
  \item CONSTRUCTED\_BY
  \item Emphasis on direction of arrow for exploration, importance of consistency
\end{itemize}

\subsection{Translation from \texttt{.dpd} to CSV files}

\section{Coq source-files to CSV}
Intention, execution, problems, solutions.

Also, how it fit in with larger, open-source projects.

\subsection{Missing Information}

\subsection{Glob Files}

\subsection{Collection}

\subsection{Merging}

\section{CSV to Neo4j}
Intention, execution, problems, solutions.

Also, how it fit in with larger, open-source projects.

\subsection{Neo4j Import Tools}

\subsection{Impact of Changes to Model}
Trade-offs, execution.

\section{Query Library}
Intention, execution, problems, solutions.

Also, how it fit in with larger, open-source projects.

\subsection{APOC}

\subsection{Additions on top of APOC}

\subsection{igraph}

\subsubsection{Terminology}

\subsubsection{Betweenness Centrality}

\subsubsection{Closeness Centrality}

\subsubsection{PageRank}

\subsubsection{Community Detection}

\subsection{Visualisation}

\subsection{R Library}

\subsection{Project Related}
Modifying make files, continuous-integration builds, editors

\section{Summary}
Features implemented, dead-ends and lessons learnt.
